%!TEX root = ../tesi-ayurveda-v1.tex

\begin{thebibliography}{3} 
\addcontentsline{toc}{chapter}{Bibliografia} 


%----------------------------------------------------------------------------------------
%	INTRO
%----------------------------------------------------------------------------------------


\bibitem{webi} Smith, J. (2005). \textit{Cherry Pie for Beginners}. Ayurvedic Point. Estrapolato da http://www.piesforeveryone.com

%----------------------------------------------------------------------------------------
%	GENERALE
%----------------------------------------------------------------------------------------


\bibitem{test} C. Tosto, A. Morandi et al. \textit{Dispense del Corso per Terapisti Ayurvedici}. Ayurvedic Point.

\bibitem{ch-chi} Charaka. \textit{Charaka Sahmita, Chikitsa Sthana}.


\bibitem{ninivaggi} F.J. Ninivaggi \textit{\={A}yurveda. Una medicina con una tradizione antica di seimila anni}. Ubaldini Editore - Roma. 2002.

\bibitem{iannaccone-ayurveda} E. Iannaccone \textit{Ayurveda. La medicina dell'armonia tra l'uomo e l'universo}. Tecniche Nuove Edizioni. 2006.

\bibitem{iannaccone-mente} E. Iannaccone \textit{I Disordini della Mente nell'\={A}yurveda}. Laksmi Edizioni. 2015.


%----------------------------------------------------------------------------------------
%	ALIMENTAZIONE
%----------------------------------------------------------------------------------------

\bibitem{bergnach} B. Bergnach, V. Ravasi. \textit{La saggezza nel cibo, l'\={A}yurveda e la cucina delle nostre nonne}. Curcu \& Genovese. 2016. 

\bibitem{joythi-nutrizione} Swami Joythimayananda. \textit{Alimentazione ayurvedica. Manuale per una nutrizione equilibrata e sana}. Macro Edizioni. 2016. 



%----------------------------------------------------------------------------------------
%	CANALI ENERGETICI SOTTILI 
%----------------------------------------------------------------------------------------

\bibitem{yoga-neti} Narayan Choyin Dorje. \textit{Manuale di yoga neti. Il tradizionale metodo yala neti per la pulizia delle vie nasali.} Tecniche nuove. 2008.


\bibitem{joythi-yoga} Swami Joythimayananda. \textit{Yoga}. Fratelli Frilli Editori. 2005. 


%----------------------------------------------------------------------------------------
%	DISTURBI DI VATA
%----------------------------------------------------------------------------------------

\bibitem{kumar} A . Vinaya Kumar. \textit{Ayurvedic Clinical Medicine}. Sri Satg\={u}ru
, Publications.

\bibitem{raghuram-manasa-def} Dr Raghuram Y.S. MD (Ay), Dr Manasa \textit{Vata disorders (Vatavyadhi): definitions, causes, symptoms}. Consultato in data Maggio 1, 2017 da https://easyayurveda.com/2017/06/05/vata-disorders-vatavyadhi/

\bibitem{raghuram-vata-causes} Dr Raghuram Y.S. MD (Ay) \textit{Different causes for Vata dosha imbalance, increase}. Consultato in data Maggio 1, 2017 da https://easyayurveda.com/2016/12/26/causes-vata-dosha-imbalance-increase/

\bibitem{raghuram-manasa-diff} Dr Raghuram Y.S. MD (Ay), Dr Manasa \textit{Difference between Vata Vyadhi and other pathological Vata manifestations}. Consultato in data Maggio 1, 2017 da https://easyayurveda.com/2017/06/05/vata-vyadhi-pathological-manifestation/


%----------------------------------------------------------------------------------------
%	LOMBALGIA - VISIONE MODERNA
%----------------------------------------------------------------------------------------

%statistiche mondiali
\bibitem{lombalgia-review} Hoy D, Bain C, Williams G, et al. \textit{A systematic review of the global prevalence of low back pain}. Arthritis Rheum. Vol. 64, nº 6, giugno 2012, pp. 2028–37, DOI:10.1002/art.34347, PMID 22231424.

\bibitem{anesthesiology} Vinod Malhotra; Yao, Fun-Sun F.; Fontes, Manuel da Costa, \textit{Yao and Artusio's Anesthesiology: Problem-Oriented Patient Management}, Hagerstwon, MD, Lippincott Williams \& Wilkins, 2011, pp. Chapter 49, ISBN 1-4511-0265-8.

\bibitem{globalburden} T Vos, \textit{Years lived with disability (YLDs) for 1160 sequelae of 289 diseases and injuries 1990–2010: a systematic analysis for the Global Burden of Disease Study 2010}.in Lancet, vol. 380, nº 9859, 15 dicembre 2012, pp. 2163–96, PMID 23245607.

\bibitem{gskreport} GSK Consumer Healthcare (GSK CH), \textit{RAPPORTO DI RICERCA. Risultati italiani sul dolore muscolo-scheletrico}. GLOBAL PAIN INDEX 2017. 


%----------------------------------------------------------------------------------------
%	LOMBALGIA - AYURVEDA
%----------------------------------------------------------------------------------------

%spiega la differenza tra trika shula e katigraha
\bibitem{insight-lom} Sajitha K. \textit{An INSIGHT in to “KATIGRAHA” (LOW BACK ACHE)}.Ancient Science of Life. 2001;21(1):16-17.


\bibitem{critical-review-lom} Gupta, S., Patil, V., \& Sharma, R. \textit{DIAGNOSIS AND MANAGEMENT OF KATISHOOLA (LOW BACK PAIN) IN AYURVEDA: A CRITICAL REVIEW}. AYUSHDHARA, 2017, 3(4).


%massaggio con sahacharadi taila per katishula
\bibitem{sahacha-massage-chronic-lom} Kumar S., Rampp T., Kessler C., Jeitler M., Dobos G. J., Lüdtke R., Meier L., and Michalsen A. \textit{Effectiveness of Ayurvedic Massage (Sahacharadi Taila) in Patients with Chronic Low Back Pain: A Randomized Controlled Trial}. The Journal of Alternative and Complementary Medicine. February 2017, 23(2): 109-115. doi:10.1089/acm.2015.0272.


%comparazione tra katibasti con mahanarayana ed esercizio fisico 
\bibitem{katibasti-esercizio-lom} Panda Ashok K., Debnath Saroj K. \textit{EFFECTIVENESS OF KATIVASTHI AND EXERCISE IN CHRONIC LOW BACK PAIN: A RANDOMIZED CONTROL STUDY}. International Journal of Research in Ayurveda \& Pharmacy, 2(2), 2011  338-342.

%efficacia di eranda muladi yapana basti
\bibitem{eranda-muladi-yapana-basti-lom} Damayanthie F. K. P., Thakar A.B., Shukla V.D. \textit{Clinical efficacy of Eranda Muladi Yapana Basti in the management of Kati Graha (Lumbar spondylosis)}. AYU 2013;34:36-41


%comparazione tra matra basti con/senza pinda sweda
\bibitem{sahacha-matra-basti-pindas-lom} Naveen B. \textit{A Comparative study of Sahachara Taila Matra Basti with and without Pinda Sweda in the management of Kati Shoola}. Dissertation, Department of Post Graduate Studies in Panchakarma S.J.G Ayurvedic Medical College \& Hospital, Koppal, 2012.


%comparazione katibasti, matra basti e patrapinda sweda
\bibitem{katibasti-matra-patrapindasweda-lom} Gupta, S., Sharma, R. \textit{Comparative clinical study of kati basti, patrapinda sveda and matra basti in kati shoola (low backache)}. Journal of Ayurveda and Holistic Medicine (JAHM), 2016, 3(6), 19-35.


%parisheka swedana con kheerabala taila
\bibitem{parisheka-swedana-ksheerabala-lom} Dilbag Singh J. \textit{ROLE OF PARISHEKA SVEDANA IN THE MANAGEMENT OF KATI GRAHA}. Dissertation, Rajiv Gandhi University of Health Science, Dept. of Post Graduate Studies in Panchakarma, S.D.M. College of Ayurveda and Hospital, Hassan, 2008.


%ruksha swedana, risultati non ottimi ma rilevanti
\bibitem{kolakulattadi-ruksha-sveda-lom} Anjaly N.V. \textit{A STUDY ON THE EFFECT OF SWEDANA WITH KOLAKULATHADI CHOORNA AND VALUKA IN KATIGRAHA}. Dissertation, Rajiv Gandhi University of Health Science, Dept. of Post Graduate Studies in Panchakarma K.V.G. Ayurvedic Medical College and Hospital, Sullia, 2010.

%----------------------------------------------------------------------------------------
%	SCIATICA
%----------------------------------------------------------------------------------------

\bibitem{agnikarma} Bakhashi B, Gupta SK, Rajagopala M, Bhuyan C. \textit{A comparative study of Agni karma with Lauha, Tamra and Panchadhatu Shalakas in Gridhrasi (Sciatica)} AYU. 2010;31:240–4

\bibitem{kabasti} Padmakiran C., Ramachandra R., Prasad U. N., Rao Niranjan1. \textit{Role of Katibasti in Gridhrasi (Lumbago Sciatica Syndrome)} International Ayurvedic Medical Journal, ISSN:2320 5091.


\bibitem{agni-kabasti} Bali Y, Vijayasarathi R, Ebnezar J, Venkatesh B. \textit{Efficacy of Agnikarma over the padakanistakam (little toe) and Katibasti in Gridhrasi: A comparative study}. Int J Ayurveda Res. 2010;1:223–30. 

\bibitem{agni-siraveda} Vaneet Kumar J, Dudhamal TS, Gupta SK, Mahanta V. \textit{A comparative clinical study of Siravedha and Agnikarma in management of Gridhrasi (sciatica)} . Ayu. 2014 Jul-Sep;35(3):270-6. doi: 10.4103/0974-8520.153743. 

\bibitem{rakta-kabasti} Singh SK, Rajoria K, Sharma RS. \textit{Comparative efficacy of Raktamokshana and Kativasti in Gridhrasi (w.s.r. to sciatica)} J Ayurveda. 2010;4:51–67.

\bibitem{reviews-grid} Arora V, Dudhamal TS, Gupta SK, Mahanta VD.\textit{ Review of researches on Grudhrasi (Sciatica)}. At IPGT and RA, Jamnagar. Indian J Ancient Med Yoga. 2013;6:31–6.

\bibitem{type-grid} Parashar S., Pandya D.H. \textit{A critical review of Vataja and Vatakaphaja Gridhrasi} International Ayurvedic Medical Journal ISSN:2320 5091

\bibitem{critical-analysis-grid} Subina S., Ananthram S., Prathibha C.K. \textit{Critical Anaalysis of Gridhrasi Chikitsa} Ayurpharm Int J Ayur Alli Sci., Vol. 5, No. 9 (2016) Pages 121 – 127, ISSN: 2278-4772.

\bibitem{tesi1} Rita V. Khagram. \textit{A comparative study of Kati Basti
and Matra Basti in the management of G\d{r}idhra\={s}i (Sciatica)}. Gujarat Ayurved University. 2004.
 

\bibitem{kabasti-eranda-grid} Greeshma G. \textit{Comparative study of Katibasti with Erandamoola Kashaya and Eranda Taila in Gridhrasi}. Dissertation, Rajiv Gandhi University of Health Science, Dept. of Panchakarma S.D.M.C.A, Karnataka, Bangalore. 2010-2011.


%qiu spiega i trattamenti - tabelle trattamenti x i due tipi di sciatica - terapie snehana e swedana
\bibitem{pancaka-grid} Imlikumba, BA Lohith, Parappagoudra Mahesh, K Singha, S Lalravi. \textit{Role of
Panchakarma in management of Gridhrasi}. J Ayurveda Integr Med Sci 2016;2:92-97.


\bibitem{management-grid} Satya P. and Sarvesh K. S. \textit{Ayurvedic Management for Gridhrasi with Special Reference to Sciatica- A Case Report}. International Journal of Advanced Ayurveda, Yoga, Unani, Siddha and Homeopathy 2015, Volume 4, Issue 1, pp. 262-265, Article ID Med-240, ISSN: 2320 – 0251.




%----------------------------------------------------------------------------------------
%	RICETTE
%----------------------------------------------------------------------------------------



%----------------------------------------------------------------------------------------
%	TRATTAMENTI
%----------------------------------------------------------------------------------------

\bibitem{tiwari} Maya Tiwari (Sri Swamini Mayatitananda). \textit{I Segreti della Guarigione Ayurvedica. La guida più completa all'antica medicina indiana}. Edizioni il Punto d'Incontro. 1998-2006.



\bibitem{joythi-abhyanga} Swami Joythimayananda. \textit{Abyangam - Massaggio Ayurvedico}. Fratelli Frilli Editori. 2007. 




\end{thebibliography} 

